\documentclass[margin,line,11pt]{res}
\usepackage{times}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,   
    urlcolor=blue,
    }
\oddsidemargin -.48in
\evensidemargin -.5in
\topmargin -.35in
\textwidth=6in
\textheight=10in
\itemsep=0in
\parsep=0in


\begin{document}

\name{\huge \sc Andrew Cooper \vspace*{.1in}}

\begin{resume}


\vspace{-0.1cm}
\section{\bf CONTACT\\INFO}
\vspace{.05in}
\begin{tabular}{@{}p{2.7in}rp{2in}}
Department of Statistics  & {\it E-mail:} & ahcooper@vt.edu \\            
Virginia Tech & {\it Homepage:} & \url{https://andrewdjac.github.io} \\   
Hutcheson Hall, 250 Drillfield Drive \\     
Blacksburg, VA 24061, USA  
\end{tabular}

\medskip
\section{\bf RESEARCH INTERESTS}

The design and analysis of computer experiments including nonstationary surrogates, 
uncertainty quantification, active learning, optimization, calibration, and reliability.

Computing and statistical inference with a focus on computer experiments and uncertainty quantification. Introducing sound statistical theory to machine learning and artificial intelligence applications for the purposes of making them more accurate, reliable, and interpretable. Bolstering technical projects by quantifying model uncertainty and risk.

\medskip
\section{\bf EDUCATION}

{\sc Virginia Polytechnic Institute and State University} \\
{\bf Ph.D.} Statistics, March 2026, advised by Robert B.~Gramacy\\
Dissertation: {\it Latent Gaussian Process Surrogates for Non-Gaussian Response Surface Modeling} \\

{\sc Duke University} \\
{\bf M.S.} Statistics, May 2020, advised by Alexander Volfovsky \\
{\bf B.S.} Statistical Science, May 2018 \\
{\bf B.S.} Computer Science, May 2018

\bigskip
\section{\bf HONORS \& AWARDS}

ASA Section on Statistics in Defense and National Security Student Paper Award; 2026 \\
Virginia Tech Jean D. Gibbons Fellowship; 2023\\
Duke Undergraduate Teaching Assistant Award Nominee; 2018\\

\medskip
\section{\bf{IN REVIEW}}

{\bf Cooper, A.}, Strait, J., Dorn, M. F., Gramacy, R. B., Parsons, B. P.,  \& Cattaneo, A. (2025). Robust Wrapped Gaussian Process Inference for Noisy Angular Data. arXiv:2512.00277. 


\medskip
\section{\bf{PEER- \\ REVIEWED \\ PAPERS}}

{\bf Cooper, A}., Booth, A. S., \& Gramacy, R. B. (2025). Modernizing full posterior inference for 
surrogate modeling of categorical-output simulation experiments. {\it Quality Engineering, 38}(1): 91-110.

Sauer, A., {\bf Cooper, A.}, \& Gramacy, R. B. (2023). Vecchia-approximated
deep Gaussian processes for computer experiments. {\it Journal of Computational
and Graphical Statistics, 32}(3), 824-837. arXiv:2204.02904


\section{OTHER \\ PUBLICATIONS}

Booth, A. S., {\bf Cooper, A.}, \& Gramacy, R. B. (2024). Nonstationary
Gaussian process surrogates. {\it Handbook of Uncertainty Quantification, to appear}; arXiv:2305.19242

\pagebreak
\section{}
\hfill {\bf Curriculum Vitae:} Andrew Cooper \  --- \  2
\medskip

\medskip
\section{\bf OPEN SOURCE SOFTWARE}

{\tt wrapgp}: An {\sf R}--package for wrapped Gaussian Process (WGP) modeling.\\
\url{https://github.com/lanl/wrapgp/tree/main}

{\tt glam}: An {\sf R}--package for Generalized Linear And Additive (``GLAM'') modeling. \\
\url{https://CRAN.R-project.org/package=glam}

\medskip
\section{\bf TALKS \& SEMINARS}
{\em Key:}
%{\bf S} $\equiv$ Seminar $\approx60$m;
{\bf IT} $\equiv$ Invited Talk $\approx30$m;
{\bf ST} $\equiv$ Speed Talk $8$m;
%{\bf CT} $\equiv$ Contributed Talk $\approx20$m; 
{\bf P} $\equiv$ Poster % $>45$m

\underline{Wrapped Gaussian Processes for RFID Localization}\\
\begin{tabular}{lrl}
IT\quad\quad & July 2025 & {\bf Quality and Productivity Research Conference}, Seattle, WA \\
\end{tabular}

\underline{Deep Gaussian Processes for Classification Tasks}\\
\begin{tabular}{lrl}
IT\quad\quad & Oct 2024 & {\bf Fall Technical Conference}, Nashville, TN \\
P\quad\quad & March 2024 & {\bf SIAM Conference on Uncertainty Quantification}, Trieste, Italy \\
P\quad\quad & March 2023 & {\bf Spring Research Conference}, Banff, Calgary \\
\end{tabular}

\underline{Robust Wing Design Optimization}\\
\begin{tabular}{lrl}
ST\quad\quad & April 2024 & {\bf Defense and Aerospace Test and Analysis Workshop}, Alexandria, VA \\
\end{tabular}

\section{OTHER \\ EMPLOYMENT}

{\sc Los Alamos National Laboratory}: statistics intern; June 2024 - Present

{\sc NASA Langley Research Center}: graduate research assistant; June - September 2023

{\sc Aerospace Corporation}: reliability and statistics intern; June - August 2022

%\medskip
%\section{OTHER \\ RESEARCH \\EXPERIENCE}

%{\sc Virginia Tech Softball}: senior analyst.  Applying Markov chain theory and Monte Carlo simulation to advise coaching decisions; 2019 - 2020

\medskip
\section{LECTURING}

{\sc STAT 3704 Statistics for Engineering Applications, Virginia Tech}: undergraduate statistics and probability course for engineering students.  Weekly 50-minute lectures; Spring 2022.

\medskip
\section{\bf SERVICE}

Mu Sigma Rho, Vice President of Virginia Tech Chapter; 2023-2025



%\medskip
%\section{\bf PROFESSIONAL MEMBERSHIP}

%American Statistical Association, Section on Physical and Engineering Sciences; 2021 - Present \\
%International Society for Bayesian Analysis; 2021 - Present \\

\end{resume}
\end{document}

